High-Dimensional Regularized Discriminant Analysis

### 2013-12-11 reports/paper-hdrda.Rnw
Updated link to supplementary material in paper.
Updated the keywords.

\begin{keyword}
\kwd{classification}
\kwd{regularized discriminant analysis}
\kwd{covariance-matrix regularization}
\kwd{high-dimensional microarray data}
\kwd{dimension reduction}
\end{keyword}

@@

Here, we propose the high-dimensional regularized discriminant analysis
(\emph{HDRDA}) classifier by first constructing a pooling matrix as a convex
combination of the covariance-matrix estimators employed in linear and quadratic
discriminant analysis. Given that the assumption of equal population covariance
matrices for linear discriminant analysis is often too stringent in practice
\citep{Clemmensen:2011kr}, our proposed classifier can relax the linearity
assumption by instead incorporating unequal covariance matrices while retaining
linear and quadratic discriminant analysis as special cases. We then establish
\emph{HDRDA} classifier by applying covariance-matrix regularization with a
parameterization that includes a large family of shrinkage methods, such as
those from \cite{Srivastava:2007ww}, \cite{Rao:1971ul}, and other methods
studied by \cite{Ramey:2013ji} and \cite{Xu:2009fl}. This regularization has the
effect of stabilizing the eigenvalues of the covariance-matrix estimators and
ensuring that the classifier is well-posed.

@@

\begin{supplement}
\sname{Supplement B}\label{suppB}
\stitle{Optimal Estimates of the HDRDA Classifier}
\slink[url]{https://github.com/ramey/paper-hdrda}
\sdescription{The graphical summary of the optimal estimates of the \emph{HDRDA} classifier from the classification study.}
\end{supplement}

>>>>

\begin{keyword}
\kwd{classification}
\kwd{regularized discriminant analysis}
\kwd{covariance-matrix regularization}
\kwd{high-dimensional multivariate analysis}
\kwd{microarray data}
\end{keyword}

@@

Here, we propose the high-dimensional regularized discriminant analysis
(\emph{HDRDA}) classifier by first constructing a pooling matrix as a convex
combination of the covariance-matrix estimators employed in linear and quadratic
discriminant analysis. Given that the assumption of equal population covariance
matrices for linear discriminant analysis is often too stringent in practice
\citep{Clemmensen:2011kr}, our proposed classifier can relax the linearity
assumption by instead incorporating unequal covariance matrices while retaining
linear and quadratic discriminant analysis as special cases. We then establish
the \emph{HDRDA} classifier by applying covariance-matrix regularization with a
parameterization that includes a large family of shrinkage methods, such as
those from \cite{Srivastava:2007ww}, \cite{Rao:1971ul}, and other methods
studied by \cite{Ramey:2013ji} and \cite{Xu:2009fl}. This regularization has the
effect of stabilizing the eigenvalues of the covariance-matrix estimators and
ensuring that the classifier is well-posed.

@@

\begin{supplement}
\sname{Supplement B}\label{suppB}
\stitle{Optimal Estimates of the HDRDA Classifier}
\slink[url]{https://github.com/ramey/paper-hdrda/tree/annals-of-applied-statistics/reports}
\sdescription{The graphical summary of the optimal estimates of the \emph{HDRDA} classifier from the classification study.}
\end{supplement}
